\TheTitle

### 2017-07-15 paper/conclusion.tex
Fixing the conclusion

In this paper, we develop a tree-based model, \mt, designed to provide git
users with a better explanation of the events occurring in a git
repository. The \mt model is rooted at the merge into the master branch
of a repository, where the leaves are the individual commits.

We implement a tool, \tool, using the \mt model, which allows a user to
filter the commits with a simple search interface. Once the user finds
the commit that they are interested in, they are provided simple
aggregated tables showing the files that were modified, the authors that
made the modifications, among other information. They are also provided
with three visualizations, a list tree, a pack tree, and a
Reingold-Tilford tree view. The list tree enables easy searching for
textual features, while the pack tree is good for visualizing the
structure of large \mt{s}, and the Reingold-Tilford tree is better
at visualizing the structure of small \mt{s}.

To ensure that our model is necessary, we evaluate the ability of users
to perform simple conceptual tasks, finding how a commit was merged into
the master branch of the Linux repository, and determining other commits
that were merged with the given merge. Finding that the participants in
our study were unable to perform this task, we compared the ability of
the participants to summarize key pieces of information aggregated in
these groups of commits. We asked for information about what files were
modified, the authors making the changes, among other tasks. Finally, we
asked the participants about their preference in tools, and which
aspects of each they preferred. We found that the participants in our
study were able to identify the correct answer more quickly and
accuractly using the \mt visualization than they were able to with
visualizations of the DAG.

Given that visualization of the model provides users with a better
understanding of events in the repository, we describe some issues with
identifying the master branch of the repository and a more generalized
approach to constructing \mt{s}. We implement the generalized approach
as a Bitbucket plugin to verify that it is able to quickly produce
results online, unlike in the implementation of \tool.

Participants in our study found them to be more enjoyable for
summarization tasks than visualizations of the DAG.\@ While there are
some issues with identifying the master branch in a robust manner, \mt
visualizations are an effective means of providing a clear conceptual
understanding and simple summarization of the events being merged into a
the master branch of a repository.

>>>>

\section{Conclusion}
\label{sec:conclusion}

In this paper, we describe a tree-based model, \mt, designed to provide git
users with a better explanation of the events occurring in a git
repository. The \mt model is rooted at the merge into the master branch
of a repository, where the leaves are the individual commits.

We implement a tool, \tool, using the \mt model, which allows a user to
filter the commits with a simple search interface. Once the desired
commit is found, \tool provides tabs for simple aggregated tables
showing the files that were modified, the authors that made the
modifications, among other information. \tool also provides three
visualizations, list tree, pack tree, and a \rt tree view. The list tree
enables easy searching for textual features, while the pack tree is good
for visualizing the structure of large \mt{s}, and the \rt tree is
better at visualizing the structure of small \mt{s}.

To ensure that our model and implementation are useful, we evaluated the
tool with a three-part user study. We tested the conceptual understanding
using the Gitk, ability to summarize merges into the master branch, and
ask for the opinions of the participants. We found that the participants
were unable to determine the commits and merges that are related to the
commits we tested with and build a conceptual understanding from the DAG
visualization. The correctness, accuracy, and timing of summarization
tasks were improved using \tool compared to Gitk. The participants
generally enjoyed the clean summarizations and simple visualizations
provided by the \mt-based visualizations in \tool.

Given that visualization of the model provides users with a better
understanding of events in the repository, we describe some issues with
identifying the master branch of the repository and a more generalized
approach to constructing \mt{s}. We implemented the generalized approach
as a Bitbucket plugin to verify that it is able to produce
visualizations for arbitrary bitbucket repositories. We found that it
was able to produce visualizations for many repositories, but was unable
to produce the visualizations of others due to rate-limiting. An
interesting side-effect of pruning the DAG is that some \mt{s} in the
repository can be visualized, while other trees are too large to
download the commit information for. The original algorithm design would
be unable to produce a visualization for any of the \mt{s}.

\mt{s} are a novel means of building a model which can be visualized and
summarized in an effective way. Participants in our study found
visualizations of the \mt to be more enjoyable for summarization tasks
than the visualizations of the DAG\@. While there are some
implementation issues with \tool, \mt visualizations are an effective
means of providing a clear conceptual understanding and simple
summarization of the events being merged into the master branch of a
repository.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "lineval.tex"
%%% End:
